Supplementary Material to ``External Prior Guided Internal Prior Learning for Real Noisy Image Denoising"

### 2016-11-16 1047_supp.tex
a
ad

\section{More Results on the 60 Cropped Images in \cite{crosschannel2016}}
In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped fromfrom \cite{crosschannel2016}. As can be seen from Fiures \ref{fig10}-\ref{fig20}, on most cases, our proposed method achieves better performance than the the competing methods. This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 36.15dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 36.20dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 36.15dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.10dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (e) CSF \cite{csf}: 35.47dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 35.94dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (g) NI \cite{neatimage}: 36.72dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 37.45dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (i) Ours: \textbf{38.09}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig10}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.97dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.99dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 36.00dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (d) MLP \cite{mlp}: 36.84dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (e) CSF \cite{csf}: 37.73dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 38.31dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (g) NI \cite{neatimage}: 37.45dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 38.01dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (i) Ours: \textbf{40.07}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C2" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig11}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.40dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 34.40dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 34.44dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (d) MLP \cite{mlp}: 33.02dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (e) CSF \cite{csf}: 33.71dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 34.03dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (g) NI \cite{neatimage}: 36.11dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 36.51dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (i) Ours: \textbf{38.32}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig12}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.89dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.92dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 35.89dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.82dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (e) CSF \cite{csf}: 36.85dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 37.35dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (g) NI \cite{neatimage}: 37.37dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 38.48dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (i) Ours: \textbf{39.66}dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig13}
\end{figure}

>>>>

\section{More Results on the 60 Cropped Images in \cite{crosschannel2016}}
In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped fromfrom \cite{crosschannel2016}. In this dataset, each scene was shot 500 times under the same camera and camera setting. The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed. As can be seen from Figures \ref{fig10}-\ref{fig20}, in most cases, our proposed method achieves better performance than the the competing methods. This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 36.15dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 36.20dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 36.15dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.10dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (e) CSF \cite{csf}: 35.47dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 35.94dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (g) NI \cite{neatimage}: 36.72dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 37.45dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (i) Ours: \textbf{38.09}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised images of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig10}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.97dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.99dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 36.00dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (d) MLP \cite{mlp}: 36.84dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (e) CSF \cite{csf}: 37.73dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 38.31dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (g) NI \cite{neatimage}: 37.45dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 38.01dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (i) Ours: \textbf{40.07}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised images of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C2" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig11}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.40dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 34.40dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 34.44dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (d) MLP \cite{mlp}: 33.02dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (e) CSF \cite{csf}: 33.71dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 34.03dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (g) NI \cite{neatimage}: 36.11dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 36.51dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (i) Ours: \textbf{38.32}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised images of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig12}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.89dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.92dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 35.89dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.82dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (e) CSF \cite{csf}: 36.85dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 37.35dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (g) NI \cite{neatimage}: 37.37dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 38.48dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (i) Ours: \textbf{39.66}dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised images of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig13}
\end{figure}
